Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-15 ms.tex
report only rms values from per-quadrant absolute zero level offset experiment
cite Schlafly+ 2014 PS1 4.5 kpc dust map instead of Green+ methods paper

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and \IRAS~100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative parametrization for the dust spectral energy distribution 
(SED) composed  of \PLANCK~and \IRAS~data. In doing so, we obtain maps of dust 
temperature and optical depth, both at $6.1'$ resolution. Because we employ a 
model that has been validated with FIRAS data down to sub-mm wavelengths, we 
expect our best-fit parameters to be useful in constructing high-resolution 
predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also measurements near the peak of the dust 
SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
derived optical depth map will serve as a useful cross-check for extinction 
estimates based directly upon optical observations of stars
\citep[e.g.][]{green14} and as a baseline for next-generation dust extinction 
maps incorporating high-resolution, full-sky infrared data sets such as 
\WISE~\citep{wright10, meisner14} and \AKARI.

@@

The formal statistical error on the best-fit 857 GHz offset is quite small, 
$\sim$0.002 MJy/sr. The systematics likely to dominate the actual uncertainty 
on our FDS-based zero level are imperfections in the \PLANCK/\verb|i100| 
zodiacal light models and the FDS99 temperature map. To quantify these 
systematic uncertainties, we split the sky into four quadrants, with the 
dividing boundaries being $b$=0$^{\circ}$ and $l$=0$^{\circ}$, 
$l$=180$^{\circ}$. We again restricted to $\mathcal{I}_{857}$$<$2.15 MJy/sr, 
and repeated the regression in each quadrant. The slopes varied from 0.948 to 
0.993, with an rms of 0.0188, while the offsets varied from $-$0.056 MJy/sr to
$+$0.089 MJy/sr, with an rms of 0.0586 MJy/sr.

>>>>

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and \IRAS~100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative parametrization for the dust spectral energy distribution 
(SED) composed  of \PLANCK~and \IRAS~data. In doing so, we obtain maps of dust 
temperature and optical depth, both at $6.1'$ resolution. Because we employ a 
model that has been validated with FIRAS data down to sub-mm wavelengths, we 
expect our best-fit parameters to be useful in constructing high-resolution 
predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also measurements near the peak of the dust 
SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
derived optical depth map will serve as a useful cross-check for extinction 
estimates based directly upon optical observations of stars
\citep[e.g.][]{schlafly14} and as a baseline for next-generation dust 
extinction maps incorporating high-resolution, full-sky infrared data sets such
as \WISE~\citep{wright10, meisner14} and \AKARI.

@@

The formal statistical error on the best-fit 857 GHz offset is quite small, 
$\sim$0.002 MJy/sr. The systematics likely to dominate the actual uncertainty 
on our FDS-based zero level are imperfections in the \PLANCK/\verb|i100| 
zodiacal light models and the FDS99 temperature map. To quantify these 
systematic uncertainties, we split the sky into four quadrants, with the 
dividing boundaries being $b$=0$^{\circ}$ and $l$=0$^{\circ}$, 
$l$=180$^{\circ}$. We again restricted to $\mathcal{I}_{857}$$<$2.15 MJy/sr, 
and repeated the regression in each quadrant. The rms of the per-quadrant 
slopes was found to be 0.0188, while the rms of the per-quadrant offsets was 
0.0586 MJy/sr.
